### 2020-03-26 CalNotes.tex
Final GIACOMO

\corr{Let us introduce a notation which will be used throughout the rest of the paper. We denote
\begin{equation}\label{eq:DefMTilde}
	\widetilde{\mathcal M}_\epl \defeq \E^{\rho^\epl}[V'(Z^\epl)\otimes V'(X^\epl)], \quad \widetilde{\mathcal M}_0 \defeq \E^{\rho^0}[V'(Z)\otimes V'(X)],
\end{equation}
\i.e., $\widetilde{\mathcal M}_\epl$ is the limit for $T \to \infty$ of the matrix $\widetilde M$ by the ergodic theorem, and $\widetilde{\mathcal M}_0$ is the limit for $\epl \to 0$ of the matrix $\widetilde{\mathcal M}_\epl$ due to Lemma \ref{lem:convMeasure}. We can now introduce the main result, namely the convergence of the filtering-based estimator to the drift coefficient of the homogenized equation.}

@@

In light of Remark \ref{rem:deltaPower}, it is fundamental to understand the behavior of the quantity
\begin{equation}
	(X_t^\epl - Z_t^\epl)^2 V''(Z_t^\epl),
\end{equation}
and of its limit for $t\to \infty$ and for $\epl \to 0$. Let us remark that due to Proposition \ref{prop:zeta} we have
\begin{equation}
	(X_t^\epl - Z_t^\epl)^2 V''(Z_t^\epl) \approx \delta^2 (B_t^\epl)^2 V''(Z_t^\epl),
\end{equation}
and therefore studying the right hand side of the approximate equality above is the goal of the upcoming discussion. The following result, whose proof is in Appendix \ref{ap:ProofsDeltaZeta}, gives a first characterization.

@@

Let us remark that the quantity appearing above hints towards the theory of homogenization. In fact, we recall that the homogenization coefficient $K$ is given by
\begin{equation}
	K = \int_0^L \left(1 + \Phi'(y)\right)^2 \mu(\d y),
\end{equation}
where $\mu$ is the marginal measure of the process $Y^\epl$ when coupled with $X^\epl$. Therefore, the next step is considering the homogenization limit, i.e., the limit of vanishing $\epl$, which is considered in the following Lemma, whose proof is given in Appendix \ref{ap:ProofsDeltaZeta}.

@@

\begin{theorem}\label{thm:mainTheorem_zeta} Let the assumptions of Lemma \ref{lem:ergodicity} and Lemma \ref{lem:quadruple} hold. Let $\widehat A^\epl_k(T)$ be defined in \eqref{eq:AHatMixed} and $\delta = \epl^\zeta$ with $\zeta \in (0,2)$. If $\widetilde M$ is invertible, then

@@

	where $\widetilde{\mathcal M}_\epl$ is defined in \eqref{eq:DefMTilde}.	Then following the proof of Theorem \ref{thm:mainTheorem} and in light of Remark \ref{rem:deltaPower}, we only need to show that if $\delta = \epl^\zeta$ with $\zeta \in (0,2)$ we have

@@

	\lim_{\epl \to 0} \mathcal A^\epl(\delta) = A, \quad \text{in law}.

@@

	&= \Sigma \E^{\rho^0} [V''(X)].

@@

	\lim_{\epl \to 0} \widetilde{\mathcal M}_\epl^{-1} = \E^{\rho^0} [V'(X) \otimes V'(X) ] \eqdef \mathcal M_0.

@@

	Therefore

@@

	\lim_{\epl \to 0} \mathcal A^\epl(\delta) = \Sigma \mathcal M_0^{-1} \E^{\rho^0} [V''(X)],

@@

In this section, we present how to correct the faulty behaviour highlighted by Theorem \ref{thm:BayesianBias} with filtering techniques. Employing the filter in the same way as for the MLE, we can modify the likelihood function and obtain 
\begin{equation}
	\widehat p(X^\epl \mid A) = \exp\left(-\frac{\widehat I(X^\epl\mid A)}{2\Sigma} \right), 
\end{equation}
where 
\begin{equation}
\begin{aligned}
	\widehat I(X^\epl \mid A) & = \int_0^T A \cdot V'(Z^\epl_t) \dd X^\epl_t + \frac12 \int_0^T \left(A \cdot V'(X^\epl_t)\right)\left(A \cdot V'(Z^\epl_t)\right) \dd t \\
	&= \widetilde h \cdot A + \frac12 A \cdot \widetilde M A.
\end{aligned}
\end{equation}
Let us remark that $\widetilde M$ is not symmetric. Nevertheless, we have that
\begin{equation}
	A \cdot \widetilde M A = A \cdot \widetilde M_S A,
\end{equation}
where $\widetilde M_S$ is the symmetric part of $\widetilde M$. Repeating the same reasoning as above, one would therefore obtain a modified posterior $\widehat \mu_{T, \epl} = \mathcal N(\widehat m_{T, \epl}, \widehat C_{T, \epl})$, whose covariance matrix and mean would be given by
\begin{equation}
\begin{aligned}
	\widehat C_{T, \epl}^{-1} &= C_0^{-1} + \frac{T}{2\Sigma} \widetilde M_S, \\
	\widehat C_{T,\epl}^{-1}\widehat m_{T,\epl} &= C_0^{-1}A_0 - \frac{T}{2\Sigma} \widetilde h. 
\end{aligned}	
\end{equation}
There is no guarantee under Assumption \ref{as:regularity} that $\widehat C_{T, \epl}$ is positive define and therefore a covariance matrix. Hence, in this Bayesian setting, we consider a different modification of the likelihood where we perturb only the vector $h$, i.e.,
\begin{equation}
	\widetilde p(X^\epl \mid A) = \exp\left(-\frac{\widetilde I(X^\epl\mid A)}{2\Sigma} \right), 
\end{equation}
where 
\begin{equation}
\begin{aligned}
	\widetilde I(X^\epl \mid A) & = \int_0^T A \cdot V'(Z^\epl_t) \dd X^\epl_t + \frac12 \int_0^T \left(A \cdot V'(X^\epl_t)\right)^2 \dd t \\
	&= \widetilde h \cdot A + \frac12 A \cdot M A.
\end{aligned}
\end{equation}
so that we obtain the modified posterior $\widetilde \mu_{T,\epl} = \mathcal N(\widetilde m_{T, \epl}, C_{T, \epl})$, whose parameters are given by
\begin{equation}
\begin{aligned}
	C_{T, \epl}^{-1} &= C_0^{-1} + \frac{T}{2\Sigma} M, \\
	C_{T,\epl}^{-1}\widetilde m_{T,\epl} &= C_0^{-1}A_0 - \frac{T}{2\Sigma} \widetilde h. 
\end{aligned}	
\end{equation}
Let us remark that the posterior $\widetilde \mu_{T,\epl}$ has the same covariance as $\mu_{T,\epl}$ and that therefore it is indeed a valid Gaussian posterior distribution. Nevertheless, in order to employ the tool of convergence introduced in Theorem \ref{thm:BayesianBias}, we need to study the properties of the MLE based on the likelihood $\widetilde p(X^\epl \mid A)$, i.e., the quantity
\begin{equation}\label{eq:AHatMixedTilde}
	\widetilde A^\epl_k(T) = - M^{-1} \widetilde h.
\end{equation}
The following theorem guarantees the unbiasedness of this estimator under a condition on the parameter $\delta$ of the filter, and we refer to Appendix \ref{ap:EstimatorTilde} for its proof.
\begin{theorem}\label{thm:mainTheoremTilde} Let the assumptions of Theorem \ref{thm:mainTheorem} hold. Then, if \corr{$\delta = \epl^\zeta$, with $\zeta \in (0, 2)$}, it holds
	\begin{equation}
	\lim_{\epl \to 0} \lim_{T \to \infty} \widetilde A^\epl_k(T) = A, \quad \text{in probability},
	\end{equation} 
	for $\widetilde A^\epl_k(T)$ defined in \eqref{eq:AHatMixedTilde}.
\end{theorem}

\corr{In light of the proof of Theorem \ref{thm:BayesianBias}, the result above guarantees that the mean of the posterior distribution $\widetilde \mu_{T, \epl}$ converges to the drift coefficient of the homogenized equation. Being the covariance matrix the same for $\mu_{T, \epl}$ and $\widetilde \mu_{T, \epl}$, it is possible to prove a positive convergence result for $\widetilde \mu_{T, \epl}$, which is given by the following Theorem.
\begin{theorem} Let the Assumptions of Theorem \ref{thm:mainTheoremTilde} hold. Then, the modified posterior measure $\widetilde\mu_{T,\epl}(\cdotp\mid X^\epl) = \mathcal N(\widetilde m_{T,\epl}, C_{T,\epl})$ satisfies
	\begin{equation}
		\lim_{\epl \to 0}\lim_{T \to \infty} \E \left[\mu_{T,\epl}\left(\{a\colon \norm{a-A}_2\geq c\}\mid X^\epl\right)\right] = 0,
	\end{equation}
	where $\E$ denotes expectation with respect to the Wiener measure and $A$ is the drift coefficient of the homogenized equation \eqref{eq:SDE_HOM}.
\end{theorem}}
\begin{proof} The proof follows from the proof of Theorem \ref{thm:BayesianBias} and from Theorem \ref{thm:mainTheoremTilde}.
\end{proof}

@@

It is relevant to study the quantities
\begin{equation}\label{eq:CalM}
\mathcal M_\epl \defeq \E^{\rho^\epl}[V'(X^\epl) \otimes V'(X^\epl)] \quad \text{and} \quad \widetilde{\mathcal M}_\epl \defeq \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(X^\epl)],
\end{equation}
which are by the ergodic theorem the time limit of the matrices appearing in the estimators $\widehat A^\epl(T)$ and $\widehat A^\epl_k(T)$, respectively. In particular, the distance between the matrices $\mathcal M_\epl$ and $\widetilde{\mathcal M}_\epl$ can be bounded, which is summarized in the following lemma.

\begin{lemma}\label{lem:distanceMandTildeM} Let the assumptions of Corollary \ref{cor:distanceZandX} hold. Then the matrices $\mathcal M_\epl$ and $\widetilde{\mathcal M}_\epl$ defined in \eqref{eq:CalM} satisfy
	\begin{equation}
	\norm{\mathcal M_\epl - \widetilde{\mathcal M}_\epl}_2 \leq C\left(\epl + \delta^{1/2}\right),
	\end{equation}
	for a constant $C > 0$ independent of $\epl$ and $\delta$.
\end{lemma}
\begin{proof} Applying Jensen's and Cauchy--Schwarz inequalities we have
	\begin{equation}
	\begin{aligned}
	\norm{\mathcal M_\epl - \widetilde{\mathcal M}_\epl}_2 &\leq \E^{\rho^\epl} \norm{\left(V'(Z^\epl) - V'(X^\epl)\right) \otimes V'(X^\epl)}_2 \\
	&\leq \left(\E^{\rho^\epl}\norm{V'(Z^\epl) - V'(X^\epl)}_2^2\right)^{1/2} \left(\E^{\rho^\epl} \norm{V'(X^\epl)}_2^{2}\right)^{1/2}.
	\end{aligned}
	\end{equation}
	The Lipschitz condition on $V'$ together with the boundedness of the moments of $X^\epl$ and Corollary \ref{cor:distanceZandX} yield for a constant $C > 0$
	\begin{equation}
	\begin{aligned}
	\norm{\mathcal M_\epl - \widetilde{\mathcal M}_\epl}_2 &\leq C\left(\E^{\rho^\epl}\abs{Z^\epl - X^\epl}^{2}\right)^{1/2} \leq C \left(\epl + \delta^{1/2} \right),
	\end{aligned}
	\end{equation}
	which is the desired result.
\end{proof}

@@

	&\partial_x \left( \left( \alpha \cdot V'(x) + \frac1\epl p'(y) \right) \eta^\epl \right) - \frac1\delta\partial_z \left( (x-z) \eta^\epl \right) \\
	&\quad + \frac1\delta \partial_b \eta^\epl  + \partial_y \left( \left( \frac1\epl \alpha \cdot V'(x) + \frac{1}{\epl^2} p'(y) \right) \eta^\epl \right) + \sigma \left( \partial_{xx}^2 \eta^\epl + \frac2\epl \partial_{xy}^2 \eta^\epl + \frac1{\epl^2} \partial_{yy}^2 \eta^\epl \right) \\

@@

	Let us introduce the notation 
	\begin{equation}
	\Delta(\epl) = \left| \sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] - \Sigma \E^{\phi^0} [V''(X)] \right|,
	\end{equation}
	and note that the aim is to show that $\lim_{\epl \to 0} \Delta(\epl) = 0$. By the triangle inequality we get
	\begin{equation}
	\begin{aligned}
	\Delta(\epl) \le& \left| \sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] - \sigma \E^{\eta^\epl} [V''(X^\epl) (1 + \Phi'(Y^\epl))^2] \right| \\
	&+ \left| \sigma \E^{\eta^\epl} [V''(X^\epl) (1 + \Phi'(Y^\epl))^2] - \Sigma \E^{\phi^0} [V''(X)] \right| \\
	\eqdef& \Delta_1(\epl) + \Delta_2(\epl).
	\end{aligned}
	\end{equation}
	We first study $\Delta_1(\epl)$ and due to the boundedness of $\Phi'$, Assumption \ref{as:regularity} and Lemma \ref{cor:distanceZandX} we have
	\begin{equation}
	\Delta_1(\epl) \le C \E^{\eta^\epl} \abs{X^\epl - Z^\epl} \le C (\delta^{1/2} + \epl) = C (\epl^{\zeta/2} + \epl),
	\end{equation}
	which implies
	\begin{equation}
	\lim_{\epl \to 0} \Delta_1(\epl) = 0.
	\end{equation}
	We now consider $\Delta_2(\epl)$. Integrating equation \eqref{eq:FPSDEquadruple} with respect to $z$ and $b$ we obtain the Fokker-Planck equation for the stationary marginal distribution $\lambda \colon \R \times [0,L]$, $\lambda = \lambda(x,y)$, of the couple $(X^\epl,Y^\epl)$
	\begin{equation}
	\begin{aligned}
	\partial_x \left( \left( \alpha \cdot V'(x) + \frac1\epl p'(y) \right) \lambda \right) + \partial_y \left( \left( \frac1\epl \alpha \cdot V'(x) + \frac{1}{\epl^2} p'(y) \right) \lambda \right) & \\
	+ \sigma \left( \partial_{xx}^2 \lambda + \partial_{xy}^2 \left( \frac2\epl \lambda \right) + \partial_{yy}^2 \left( \frac{1}{\epl^2} \lambda \right) \right) &= 0,
	\end{aligned}
	\end{equation}
	whose solution is given by
	\begin{equation}
	\lambda(x,y) = \frac{1}{C_\lambda} \exp \left\{ - \frac\alpha\sigma V(x) - \frac1\sigma p(y) \right\},
	\end{equation}
	where
	\begin{equation}
	\begin{aligned}
	C_{\lambda} &= \int_\R \int_0^L \exp \left\{ - \frac\alpha\sigma V(x) - \frac1\sigma p(y) \right\} \dd x \dd y \\
	&= \left( \int_\R \exp \left\{ - \frac\alpha\sigma V(x) \right\} \dd x \right) \left( \int_0^L \exp \left\{ - \frac1\sigma p(y) \right\} \dd y \right) \\
	&\eqdef C_{\lambda_x} C_{\lambda_y}.
	\end{aligned}
	\end{equation}
	Therefore, by equations \eqref{eq:SDE_HOM}, \eqref{eq:K_HOM} and \eqref{eq:phi0} we have
	\begin{equation}
	\begin{aligned}
	\sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] &= \sigma \int_\R \int_0^L V''(x) (1 + \Phi'(y))^2 \frac{1}{C_\lambda} \exp \left\{ - \frac\alpha\sigma V(x) - \frac1\sigma p(y) \right\} \dd x \dd y \\
	&= \sigma \left( \int_\R V''(x) \frac{1}{C_{\lambda_x}} \exp \left\{ - \frac\alpha\sigma V(x) \right\} \dd x \right) \\
	&\qquad \qquad \times \left( \int_0^L (1+\Phi'(y))^2 \frac{1}{C_{\lambda_y}} \exp \left\{ - \frac1\sigma p(y) \right\} \dd y \right) \\
	&= \sigma K \E^{\phi^0}[V''(X)] = \Sigma \E^{\phi^0}[V''(X)],
	\end{aligned}
	\end{equation}
	which shows that $\Delta_2(\epl) = 0$ and completes the proof. \qed

\section{Proof of Theorem \ref{thm:mainTheoremTilde}}\label{ap:EstimatorTilde}
Let us consider the estimator defined in \eqref{eq:AHatMixedTilde}, that is
\begin{equation}
	\widetilde A^\epl_k(T) = -M^{-1}\widetilde h,
\end{equation}
where the matrix $M$ is taken from \eqref{eq:MandH} and the vector $\widetilde{h}$ is taken from \eqref{eq:MandHTilde}. We prove here Theorem \ref{thm:mainTheoremTilde}, i.e., the unbiasedness of this estimator. Let us consider a couple $(X^\epl, Z^\epl)^\top$.

We can finally prove the unbiasedness of the estimator $\widetilde A^\epl_k(T)$.

>>>>

\corr{Let us introduce a notation which will be used throughout the rest of the paper. We denote
\begin{equation}\label{eq:DefCalMTilde}
	\widetilde{\mathcal M}_\epl \defeq \E^{\rho^\epl}[V'(Z^\epl)\otimes V'(X^\epl)], \quad \widetilde{\mathcal M}_0 \defeq \E^{\rho^0}[V'(Z)\otimes V'(X)],
\end{equation}
\i.e., $\widetilde{\mathcal M}_\epl$ is the limit for $T \to \infty$ of the matrix $\widetilde M$ by the ergodic theorem, and $\widetilde{\mathcal M}_0$ is the limit for $\epl \to 0$ of the matrix $\widetilde{\mathcal M}_\epl$ due to Lemma \ref{lem:convMeasure}. For completeness, we introduce here the symmetric matrices $\mathcal M_\epl$ and $\mathcal M_0$ which are defined as
\begin{equation}\label{eq:DefCalM}
	\mathcal M_\epl \defeq \E^{\rho^\epl}[V'(X^\epl)\otimes V'(X^\epl)], \quad \mathcal M_0 \defeq \E^{\rho^0}[V'(X)\otimes V'(X)],
\end{equation}
and which will be employed in the following. We can now introduce the main result, namely the convergence of the filtering-based estimator to the drift coefficient of the homogenized equation.}

@@

In light of Remark \ref{rem:deltaPower}, it is fundamental to understand the behavior of the quantity
\begin{equation}
	\frac1\delta (X_t^\epl - Z_t^\epl)^2 V''(Z_t^\epl),
\end{equation}
and of its limit for $t\to \infty$ and for $\epl \to 0$. Let us remark that due to Proposition \ref{prop:zeta} we have
\begin{equation}
	\frac1\delta (X_t^\epl - Z_t^\epl)^2 V''(Z_t^\epl) \approx \delta (B_t^\epl)^2 V''(Z_t^\epl),
\end{equation}
and therefore studying the right hand side of the approximate equality above is the goal of the upcoming discussion. The following result, whose proof is in Appendix \ref{ap:ProofsDeltaZeta}, gives a first characterization.

@@

Let us remark that the quantity appearing above hints towards the theory of homogenization. In fact, we recall that the homogenization coefficient $K$ is given by
\begin{equation}
	K = \int_0^L \left(1 + \Phi'(y)\right)^2 \mu(\d y),
\end{equation}
where $\mu$ is the marginal measure of the process $Y^\epl$ when coupled with $X^\epl$. Therefore, the next step is the homogenization limit, i.e., the limit of vanishing $\epl$, which is considered in the following Lemma, and whose proof is given in Appendix \ref{ap:ProofsDeltaZeta}.

@@

\begin{theorem}\label{thm:mainTheorem_zeta} Let the assumptions of Lemma \ref{lem:ergodicity} and Lemma \ref{lem:quadruple_convergence} hold. Let $\widehat A^\epl_k(T)$ be defined in \eqref{eq:AHatMixed} and $\delta = \epl^\zeta$ with $\zeta \in (0,2)$. If $\widetilde M$ is invertible, then

@@

	where $\widetilde{\mathcal M}_\epl$ is defined in \eqref{eq:DefCalMTilde}.	Then following the proof of Theorem \ref{thm:mainTheorem} and in light of Remark \ref{rem:deltaPower}, we only need to show that if $\delta = \epl^\zeta$ with $\zeta \in (0,2)$ we have

@@

	\lim_{\epl \to 0} \mathcal A^\epl(\delta) = A, \quad \text{in probability}.

@@

	&= \Sigma \E^{\phi^0} [V''(X)].

@@

	\lim_{\epl \to 0} \widetilde{\mathcal M}_\epl = \mathcal M_0,

@@

	where $\mathcal M_0$ is defined in \eqref{eq:DefCalM}. Therefore

@@

	\lim_{\epl \to 0} \mathcal A^\epl(\delta) = \Sigma \mathcal M_0^{-1} \E^{\phi^0} [V''(X)],

@@

In this section, we present how to correct the faulty behaviour highlighted by Theorem \ref{thm:BayesianBias} with filtering techniques. Employing the filter in the same way as for the MLE, we can modify the likelihood function and obtain 
	\widehat p(X^\epl \mid A) = \exp\left(-\frac{\widehat I(X^\epl\mid A)}{2\Sigma} \right), 
	\widehat I(X^\epl \mid A) & = \int_0^T A \cdot V'(Z^\epl_t) \dd X^\epl_t + \frac12 \int_0^T \left(A \cdot V'(X^\epl_t)\right)\left(A \cdot V'(Z^\epl_t)\right) \dd t \\
	&= \widetilde h \cdot A + \frac12 A \cdot \widetilde M A.
Let us remark that $\widetilde M$ is not symmetric. Nevertheless, we have that
	A \cdot \widetilde M A = A \cdot \widetilde M_S A,
where $\widetilde M_S$ is the symmetric part of $\widetilde M$. Repeating the same reasoning as above, one would therefore obtain a modified posterior $\widehat \mu_{T, \epl} = \mathcal N(\widehat m_{T, \epl}, \widehat C_{T, \epl})$, whose covariance matrix and mean would be given by
	\widehat C_{T, \epl}^{-1} &= C_0^{-1} + \frac{T}{2\Sigma} \widetilde M_S, \\
	\widehat C_{T,\epl}^{-1}\widehat m_{T,\epl} &= C_0^{-1}A_0 - \frac{T}{2\Sigma} \widetilde h. 
There is no guarantee under Assumption \ref{as:regularity} that $\widehat C_{T, \epl}$ is positive define and therefore a covariance matrix. Hence, in this Bayesian setting, we consider a different modification of the likelihood where we perturb only the vector $h$, i.e.,
	\widetilde p(X^\epl \mid A) = \exp\left(-\frac{\widetilde I(X^\epl\mid A)}{2\Sigma} \right), 
	\widetilde I(X^\epl \mid A) & = \int_0^T A \cdot V'(Z^\epl_t) \dd X^\epl_t + \frac12 \int_0^T \left(A \cdot V'(X^\epl_t)\right)^2 \dd t \\
	&= \widetilde h \cdot A + \frac12 A \cdot M A.
so that we obtain the modified posterior $\widetilde \mu_{T,\epl} = \mathcal N(\widetilde m_{T, \epl}, C_{T, \epl})$, whose parameters are given by
	C_{T, \epl}^{-1} &= C_0^{-1} + \frac{T}{2\Sigma} M, \\
	C_{T,\epl}^{-1}\widetilde m_{T,\epl} &= C_0^{-1}A_0 - \frac{T}{2\Sigma} \widetilde h. 
Let us remark that the posterior $\widetilde \mu_{T,\epl}$ has the same covariance as $\mu_{T,\epl}$ and that therefore it is indeed a valid Gaussian posterior distribution. Nevertheless, in order to employ the tool of convergence introduced in Theorem \ref{thm:BayesianBias}, we need to study the properties of the MLE based on the likelihood $\widetilde p(X^\epl \mid A)$, i.e., the quantity
\begin{equation}\label{eq:AHatMixedTilde}
	\widetilde A^\epl_k(T) = - M^{-1} \widetilde h.
The following theorem guarantees the unbiasedness of this estimator under a condition on the parameter $\delta$ of the filter.
\begin{theorem}\label{thm:mainTheoremTilde} Let the assumptions of Theorem \ref{thm:mainTheorem} hold. Then, if \corr{$\delta = \epl^\zeta$, with $\zeta \in (0, 2)$}, it holds
	\lim_{\epl \to 0} \lim_{T \to \infty} \widetilde A^\epl_k(T) = A, \quad \text{in probability},
	for $\widetilde A^\epl_k(T)$ defined in \eqref{eq:AHatMixedTilde}.
\begin{proof} We first consider the difference between the two estimators $\widetilde A^\epl_k(T)$ and $\widehat A^\epl_k(T)$. In particular, the ergodic theorem and an algebraic equality imply
	\lim_{T \to \infty} \left(\widetilde A^\epl_k(T) - \widehat A^\epl_k(T)\right) &= \left(\mathcal M_\epl^{-1} - \widetilde{\mathcal M}_\epl^{-1}\right) \lim_{T \to \infty}\widetilde h \\
	&= \mathcal M_\epl^{-1}\left(\mathcal M_\epl - \widetilde{\mathcal M}_\epl\right)  \widetilde{\mathcal M}_\epl^{-1} \lim_{T \to \infty} \widetilde h\\
	&= \mathcal M_\epl^{-1}\left(\mathcal M_\epl - \widetilde{\mathcal M}_\epl\right)\lim_{T \to \infty} \widehat A^\epl_k(T),
	almost surely, where $\mathcal M_\epl$ and $\widetilde{\mathcal M}_\epl$ are defined in \eqref{eq:DefCalM} and \eqref{eq:DefCalMTilde}, respectively. Therefore, due to Assumption \ref{as:regularity} which allows controlling the norm of $\mathcal M_\epl^{-1}$ and due to Lemma \ref{lem:distanceMandTildeM} we have for a constant $C > 0$
	\begin{equation}\label{eq:DistATildeAHat}
	\lim_{T \to \infty} \norm{\widetilde A^\epl_k(T) - \widehat A^\epl_k(T)}_2 \leq C \left(\epl + \delta^{1/2} \right).
	Let us remark that $\widehat A^\epl_k(T)$ has a bounded norm for $\epl$ sufficiently small due to Theorem \ref{thm:mainTheorem}. Now, the triangle inequality yields
	\norm{\widetilde A^\epl_k(T) - A}_2 \leq \norm{\widetilde A^\epl_k(T) - \widehat A^\epl_k(T)}_2 + \norm{\widehat A^\epl_k(T) - A}_2.
	Therefore, due to Theorem \ref{thm:mainTheorem_zeta}, the inequality \eqref{eq:DistATildeAHat} and since $\delta = \mathcal O(\epl^\zeta)$, the desired result holds.
In light of the proof of Theorem \ref{thm:BayesianBias}, the result above guarantees that the mean of the posterior distribution $\widetilde \mu_{T, \epl}$ converges to the drift coefficient of the homogenized equation. Being the covariance matrix the same for $\mu_{T, \epl}$ and $\widetilde \mu_{T, \epl}$, it is possible to prove a positive convergence result for $\widetilde \mu_{T, \epl}$, which is given by the following Theorem.
\begin{theorem} Let the Assumptions of Theorem \ref{thm:mainTheoremTilde} hold. Then, the modified posterior measure $\widetilde\mu_{T,\epl}(\cdotp\mid X^\epl) = \mathcal N(\widetilde m_{T,\epl}, C_{T,\epl})$ satisfies
		\lim_{\epl \to 0}\lim_{T \to \infty} \E \left[\mu_{T,\epl}\left(\{a\colon \norm{a-A}_2\geq c\}\mid X^\epl\right)\right] = 0,
	where $\E$ denotes expectation with respect to the Wiener measure and $A$ is the drift coefficient of the homogenized equation \eqref{eq:SDE_HOM}.
\end{theorem}}
\begin{proof} The proof follows from the proof of Theorem \ref{thm:BayesianBias} and from Theorem \ref{thm:mainTheoremTilde}.

@@

Let us conclude with a last preliminary estimate concerning the matrices $\widetilde{\mathcal M}_\epl$ and $\mathcal M_\epl$ defined in \eqref{eq:DefCalMTilde} and \eqref{eq:DefCalM}, respectively.

\begin{lemma}\label{lem:distanceMandTildeM} Let the assumptions of Corollary \ref{cor:distanceZandX} hold. Then the matrices $\mathcal M_\epl$ and $\widetilde{\mathcal M}_\epl$ satisfy
	\begin{equation}
	\norm{\mathcal M_\epl - \widetilde{\mathcal M}_\epl}_2 \leq C\left(\epl + \delta^{1/2}\right),
	\end{equation}
	for a constant $C > 0$ independent of $\epl$ and $\delta$.
\end{lemma}
\begin{proof} Applying Jensen's and Cauchy--Schwarz inequalities we have
	\begin{equation}
	\begin{aligned}
	\norm{\mathcal M_\epl - \widetilde{\mathcal M}_\epl}_2 &\leq \E^{\rho^\epl} \norm{\left(V'(Z^\epl) - V'(X^\epl)\right) \otimes V'(X^\epl)}_2 \\
	&\leq \left(\E^{\rho^\epl}\norm{V'(Z^\epl) - V'(X^\epl)}_2^2\right)^{1/2} \left(\E^{\rho^\epl} \norm{V'(X^\epl)}_2^{2}\right)^{1/2}.
	\end{aligned}
	\end{equation}
	The Lipschitz condition on $V'$ together with the boundedness of the moments of $X^\epl$ and Corollary \ref{cor:distanceZandX} yield for a constant $C > 0$
	\begin{equation}
	\begin{aligned}
	\norm{\mathcal M_\epl - \widetilde{\mathcal M}_\epl}_2 &\leq C\left(\E^{\rho^\epl}\abs{Z^\epl - X^\epl}^{2}\right)^{1/2} \leq C \left(\epl + \delta^{1/2} \right),
	\end{aligned}
	\end{equation}
	which is the desired result.
\end{proof}

@@

	&\partial_x \left( \left( \alpha \cdot V'(x) + \frac1\epl p'(y) \right) \eta^\epl \right) + \frac1\delta\partial_z \left( (z-x) \eta^\epl \right) \\
	&\quad + \frac1\delta \partial_b (b\eta^\epl)  + \partial_y \left( \left( \frac1\epl \alpha \cdot V'(x) + \frac{1}{\epl^2} p'(y) \right) \eta^\epl \right) + \sigma \left( \partial_{xx}^2 \eta^\epl + \frac2\epl \partial_{xy}^2 \eta^\epl + \frac1{\epl^2} \partial_{yy}^2 \eta^\epl \right) \\

@@

	Let us introduce the notation 
	\begin{equation}
	\Delta(\epl) = \left| \sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] - \Sigma \E^{\phi^0} [V''(X)] \right|,
	\end{equation}
	and note that the aim is to show that $\lim_{\epl \to 0} \Delta(\epl) = 0$. By the triangle inequality we get
	\begin{equation}
	\begin{aligned}
	\Delta(\epl) \le& \left| \sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] - \sigma \E^{\eta^\epl} [V''(X^\epl) (1 + \Phi'(Y^\epl))^2] \right| \\
	&+ \left| \sigma \E^{\eta^\epl} [V''(X^\epl) (1 + \Phi'(Y^\epl))^2] - \Sigma \E^{\phi^0} [V''(X)] \right| \\
	\eqdef& \Delta_1(\epl) + \Delta_2(\epl).
	\end{aligned}
	\end{equation}
	We first study $\Delta_1(\epl)$ and due to the boundedness of $\Phi'$, Assumption \ref{as:regularity} and Lemma \ref{cor:distanceZandX} we have
	\begin{equation}
	\Delta_1(\epl) \le C \E^{\eta^\epl} \abs{X^\epl - Z^\epl} \le C (\delta^{1/2} + \epl) = C (\epl^{\zeta/2} + \epl),
	\end{equation}
	which implies
	\begin{equation}
	\lim_{\epl \to 0} \Delta_1(\epl) = 0.
	\end{equation}
	We now consider $\Delta_2(\epl)$. Integrating equation \eqref{eq:FPSDEquadruple} with respect to $z$ and $b$ we obtain the Fokker-Planck equation for the stationary marginal distribution $\lambda \colon \R \times [0,L]$, $\lambda = \lambda(x,y)$, of the couple $(X^\epl,Y^\epl)$
	\begin{equation}
	\begin{aligned}
	\partial_x \left( \left( \alpha \cdot V'(x) + \frac1\epl p'(y) \right) \lambda \right) + \partial_y \left( \left( \frac1\epl \alpha \cdot V'(x) + \frac{1}{\epl^2} p'(y) \right) \lambda \right) & \\
	+ \sigma \left( \partial_{xx}^2 \lambda + \partial_{xy}^2 \left( \frac2\epl \lambda \right) + \partial_{yy}^2 \left( \frac{1}{\epl^2} \lambda \right) \right) &= 0,
	\end{aligned}
	\end{equation}
	whose solution is given by
	\begin{equation}
	\lambda(x,y) = \frac{1}{C_\lambda} \exp \left( - \frac\alpha\sigma V(x) - \frac1\sigma p(y) \right),
	\end{equation}
	where
	\begin{equation}
	\begin{aligned}
	C_{\lambda} &= \int_\R \int_0^L \exp \left( - \frac\alpha\sigma V(x) - \frac1\sigma p(y) \right) \dd x \dd y \\
	&= \left( \int_\R \exp \left( - \frac\alpha\sigma V(x) \right) \dd x \right) \left( \int_0^L \exp \left( - \frac1\sigma p(y) \right) \dd y \right) \\
	&\eqdef C_{\lambda_x} C_{\lambda_y}.
	\end{aligned}
	\end{equation}
	Therefore, by equations \eqref{eq:SDE_HOM}, \eqref{eq:K_HOM} and \eqref{eq:phi0} we have
	\begin{equation}
	\begin{aligned}
	\sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] &= \sigma \int_\R \int_0^L V''(x) (1 + \Phi'(y))^2 \frac{1}{C_\lambda} \exp \left( - \frac\alpha\sigma V(x) - \frac1\sigma p(y) \right) \dd x \dd y \\
	&= \sigma \left( \int_\R V''(x) \frac{1}{C_{\lambda_x}} \exp \left( - \frac\alpha\sigma V(x) \right) \dd x \right) \\
	&\qquad \qquad \times \left( \int_0^L (1+\Phi'(y))^2 \frac{1}{C_{\lambda_y}} \exp \left( - \frac1\sigma p(y) \right) \dd y \right) \\
	&= \sigma K \E^{\phi^0}[V''(X)] = \Sigma \E^{\phi^0}[V''(X)],
	\end{aligned}
	\end{equation}
	which shows that $\Delta_2(\epl) = 0$ and completes the proof. \qed 
\end{appendices}
